% !TEX root = ./resume.tex
%-------------------------
% Resume in Latex
% Author : Jenul Ferdinand
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{extarticle}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% ---------------------------------------------------------------------------- %
%                                 FONT OPTIONS                                 %
% ---------------------------------------------------------------------------- %

\usepackage[sfdefault]{sourcesanspro}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\familydefault}{\sfdefault}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \rmfamily\fontfamily{bch}\selectfont\raggedright\large
}{}{0em}{\vspace{-8pt}}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


% ---------------------------------------------------------------------------- %
%                                CUSTOM COMMANDS                               %
% ---------------------------------------------------------------------------- %

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


% ---------------------------------------------------------------------------- %
%                              RESUME STARTS HERE                              %
% ---------------------------------------------------------------------------- %

\begin{document}

% ----------------------------------- TITLE ---------------------------------- %
\begin{center}
    % Name (serif Charter)
    {\rmfamily\fontfamily{bch}\selectfont\bfseries\Huge Jenul Ferdinand} \\[4pt]
    
    % Contact info (sans-serif)
    {\sffamily\small
    +61 405 546 209 $|$ 
    \href{mailto:jenul15ferdinand@gmail.com}{jenul15ferdinand@gmail.com} $|$ 
    Australian Citizen}
    
    % Location (sans-serif)
    {\sffamily\small Knoxfield, Victoria, 3180}
\end{center}

\section{\textbf{Summary}}
  \resumeSubHeadingListStart
  \item \small
  Graduate Engineer $|$ Field Operations \& Systems Integration | Reliable and proactive professional with strong hands-on experience in Linux systems, network telemetry, and hardware-software integration. Proven leadership experience managing teams and training staff. Passionate about all things tech and loves fixing, automating, and optimising.
  \resumeSubHeadingListEnd

% --------------------------------- EDUCATION -------------------------------- %
\section{\textbf{Education}}
	\resumeSubHeadingListStart
		\item
		\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\small Bachelor of Computer Science at Monash University, Clayton Campus & Graduating November 2026
		\end{tabular*}\vspace{-4pt}
	\resumeSubHeadingListEnd

% -------------------------------- EXPERIENCE -------------------------------- %
\section{\textbf{Experience}}
  \resumeSubHeadingListStart

    \vspace{3pt}

    % ! Monash Connected Autonomous Vehicle
    \resumeSubheading
    {Systems Engineer}{August 2025 -- Present}
    {Monash Connected Autonomous Vehicle (student team)}{Clayton, VIC}
      \resumeItemListStart
        \resumeItem{Building a SIL simulation framework bridging the ROS 2 autonomous vehicle stack with a ride-hailing backend.}
        \resumeItem{Engineered vehicle telemetry systems, providing data transmission between vehicle and monitoring software.}
        \resumeItem{Managed hardware-software integration, diagnosing connection faults with ROS 2 and external network interfaces.}
        \resumeItem{Authored a technical proposal and feasibility analysis, utilising the Spiral Model to mitigate integration risks.}
        \resumeItem{Architecting the data pipeline, utilising event streaming for vehicle route performance and emissions data.}
      \resumeItemListEnd

    \vspace{3pt}

	  % ! Computer Science Intern - Hawthorn FC
	  \resumeSubheading
    {Intern}{August 2025 -- October 2025}
    {Hawthorn Football Club}{Mulgrave, VIC}
      \resumeItemListStart
        \resumeItem{Engineered a workflow optimisation solution to facilitate analysis for the coaches, supporting match-day preparation.}
        \resumeItem{Facilitated the integration of enterprise cloud systems, enabling conversational AI with transactional AFL data.}
        \resumeItem{Conducted technical training sessions for non-technical coaching staff, simplifying complex topics.}
        \resumeItem{Collaborated with the GM of Tech \& Data to identify process bottlenecks and deliver automated tooling solutions.}
        \resumeItem{Reduced manual data processing time for analysts by developing efficient sub-agent workflows for reporting.}
      \resumeItemListEnd

    \vspace{3pt}

    % ! Automation Developer - Digimaker
    \resumeSubheading
    {GAS Automation Developer}{March 2025 -- June 2025}
    {Digimaker}{Eastern Suburbs, VIC}
      \resumeItemListStart
        \resumeItem{Identified a bottleneck in the student reporting process and engineered an automation to generate PDF reports.}
        \resumeItem{Wrote JavaScript code in the Google Apps Script (GAS) environment for a zero-cost student reporting solution.}
        \resumeItem{Optimised script execution flow to handle high-volume batch processing within the strict execution time limits.}
        \resumeItem{Deployed a web interface allowing non-technical admins to trigger report generation and manage student data.}
        \resumeItem{Implemented CI/CD using Github Actions, utilising clasp and git for local development and version control.}
      \resumeItemListEnd

    \vspace{3pt}

    % ! Monash Innovation Guarantee
		\resumeSubheading
		{Intern}{January 2025}
		{UNICEF}{Docklands, VIC}
			\resumeItemListStart
        \resumeItem{Designed a secure SaaS architecture for UNICEF's uSupport platform to integrate third-party services.}
        \resumeItem{Modeled API integration flows to enable secure data exchange between external apps and the core platform.}
        \resumeItem{Presented the technical roadmap to stakeholders, awarded with a High Distinction for the solution's feasibility.}
			\resumeItemListEnd

    \vspace{3pt}

    % ! Programming Tutor - Digimaker
    \resumeSubheading
    {Technology Mentor}{October 2024 -- Present}
    {Digimaker}{Eastern Suburbs, VIC}
      \resumeItemListStart
      	\resumeItem{Delivered technical training to diverse groups, breaking down complex logic into clear, actionable instructions.}
        \resumeItem{Acted as a key escalation point for students, troubleshooting logic errors and debugging code in real-time.}
        \resumeItem{Maintained high service standards with a high retention rate, ensuring positive parent/student relationships.}
        \resumeItem{Schools: McKinnon PS, Leibler Yavneh College, Ruskin Park PS, Mulgrave PS, Burwood East PS, Greythorn PS.}
      \resumeItemListEnd

    \vspace{3pt}

    % ! WIRED (Faculty of Information Technology)
		\resumeSubheading
    {Project Lead}{May 2024 -- June 2025}
    {Faculty of Information Technology Society (student society)}{Clayton, VIC}
			\resumeItemListStart
				\resumeItem{Directed a team of 8 staff/students, managing rosters, timelines, and deliverables using Jira.}
				\resumeItem{Coordinated logistics for student projects, ensuring resources were delivered on time and within scope.}
        \resumeItem{Facilitated a productive and inclusive team environment, prioritising time management to fit the busy uni schedule.}
				\resumeItem{Oversaw project timelines using Jira, defining \& monitoring issues, epics, and sprint goals.}
			\resumeItemListEnd

  \resumeSubHeadingListEnd

% --------------------------------- PROJECTS --------------------------------- %
\section{\textbf{Projects}}
	\resumeSubHeadingListStart

    % ! Markdown to Data Project
		\resumeProjectHeading 
			{Chariot: A SIL Simulation Framework for Autonomous Vehicle Ride-Hailing}{}
			\resumeItemListStart
				\resumeItem{Associated with Monash Connected Autonomous Vehicle.}
			\resumeItemListEnd

    \vspace{3pt}
    
    % ! Markdown to Data Project
		\resumeProjectHeading 
			{md2data: A Tool to Convert Markdown Documents into Structured Data}{\href{https://www.npmjs.com/package/md2data}{\textit{\underline{\smash{npm}}}} \ \ \href{https://pypi.org/project/md2data/}{\textit{\underline{\smash{PyPi}}}} \ \
      \href{https://crates.io/crates/md2data}{\textit{\underline{Crates.io}}} \ \
      \href{https://github.com/jenul-ferdinand/md2data}{\textit{\underline{GitHub}}}}
			\resumeItemListStart
				\resumeItem{A high-performance library and CLI tool to convert markdown into JSON, TOML, YAML, or XML.}
        \resumeItem{Wrote parsing logic in Rust by constructing an Abstract Syntax Tree, utilising the pulldown-cmark pull parser.}
			\resumeItemListEnd

    \vspace{3pt}
		
		% ! MonSTAR
		\resumeProjectHeading 
			{MonSTAR: Monash University's Open-Source Course Review and Search Platform}{\href{https://monstar.wired.org.au}{\textit{\underline{Website}}} \ \ \href{https://github.com/wiredmonash/monstar}{\textit{\underline{GitHub}}}}
			\resumeItemListStart
				\resumeItem{A digital platform built for Monash University students to easily browse and review subjects and electives.}
        \resumeItem{Maintains average 1,000+ monthly visits with official endorsement from Monash University's IT Faculty.}
			\resumeItemListEnd
			
	\resumeSubHeadingListEnd

% ------------------------ LICENSES AND CERTIFICATIONS ----------------------- %
\section{\textbf{Licenses}}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \item{
        \begin{tabularx}{\linewidth}{@{}l@{\hspace{0.5cm}}X@{}}
          \textit{Australian Computer Society} & Associate Member \\[2pt]
          \textit{Victorian Government} & Working with Children Check \\[2pt]
          \textit{Victorian Driver's License}
        \end{tabularx}
      }
    }
  \end{itemize}
% ----------------------------- TECHNICAL SKILLS ----------------------------- %
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textit{Systems \& Tools:}{ Linux (Ubuntu/Debian), Bash Scripting, Network Telemetry (WebSockets/HTTP), AWS/GCP, Git}\\
     \textit{Core Competencies:}{ Technical Troubleshooting, Team Leadership, Stakeholder Communication, System Integration.}\\
     \textit{Languages:}{ Python, Rust, TypeScript (Scripting \& Automation Focused)}
    }}
 \end{itemize}

\end{document}
