%-------------------------
% Resume in Latex
% Author : Jenul Ferdinand
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{extarticle}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% ---------------------------------------------------------------------------- %
%                                 FONT OPTIONS                                 %
% ---------------------------------------------------------------------------- %

\usepackage[sfdefault]{sourcesanspro}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\familydefault}{\sfdefault}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \rmfamily\fontfamily{bch}\selectfont\raggedright\large
}{}{0em}{\vspace{-8pt}}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


% ---------------------------------------------------------------------------- %
%                                CUSTOM COMMANDS                               %
% ---------------------------------------------------------------------------- %

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


% ---------------------------------------------------------------------------- %
%                              RESUME STARTS HERE                              %
% ---------------------------------------------------------------------------- %

\begin{document}

% ----------------------------------- TITLE ---------------------------------- %
\begin{center}
    % Name (serif Charter)
    {\rmfamily\fontfamily{bch}\selectfont\bfseries\Huge Jenul Ferdinand} \\[4pt]
    
    % Contact info (sans-serif)
    {\sffamily\small
    +61 405 546 209 $|$ 
    \href{mailto:jenul15ferdinand@gmail.com}{jenul15ferdinand@gmail.com} $|$ 
    \href{https://linkedin.com/in/jenul-ferdinand}{LinkedIn} $|$
    \href{https://github.com/jenul-ferdinand}{GitHub}} \\[2pt]
    
    % Location (sans-serif)
    {\sffamily\small Australian Citizen | Knoxfield, Victoria, 3180}
\end{center}

% --------------------------------- EDUCATION -------------------------------- %
\section{\textbf{Education}}
	\resumeSubHeadingListStart
		\item
		\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\small Bachelor of Computer Science | Monash University | Clayton Campus & Studying
		\end{tabular*}\vspace{-7pt}
	\resumeSubHeadingListEnd

% --------------------------------- PROJECTS --------------------------------- %
\section{\textbf{Projects}}
	\resumeSubHeadingListStart
		
		% ! MonSTAR
		\resumeProjectHeading 
			{MonSTAR: Monash University's Open-Source Course Review and Search Platform}{\href{https://monstar.wired.org.au}{\textit{\underline{Website}}} \ \ \href{https://github.com/wiredmonash/monstar}{\textit{\underline{GitHub}}}}
			\resumeItemListStart
				\resumeItem{A digital platform built for Monash University students to easily browse and review subjects and electives.}
        \resumeItem{Maintains average 1,000+ monthly visits with official endorsement from the Monash IT Faculty.}
				\resumeItem{Developed the backend using Node.js and MongoDB, implementing RESTful API endpoints.}
				\resumeItem{Developed a reactive frontend using Angular with a Model-View-Controller architecture.}
        \resumeItem{Designed WebCoLa course progression graphs using requisites data from backend APIs.}
				\resumeItem{Populated the MongoDB Atlas database using scraped course and subject data.}
        \resumeItem{Optimised GEO/SEO strategies to maximise search visibility across 10,000+ generated pages.}
			\resumeItemListEnd

    \vspace{3pt}

    % ! Markdown to Data Project
		\resumeProjectHeading 
			{md2data: A Tool to Convert Markdown Documents into Structured Data}{\href{https://www.npmjs.com/package/md2data}{\textit{\underline{\smash{npm}}}} \ \ \href{https://pypi.org/project/md2data/}{\textit{\underline{\smash{PyPi}}}} \ \
      \href{https://crates.io/crates/md2data}{\textit{\underline{Crates.io}}} \ \
      \href{https://github.com/jenul-ferdinand/md2data}{\textit{\underline{GitHub}}}}
			\resumeItemListStart
				\resumeItem{A high-performance library and CLI tool that can convert markdown into either JSON, TOML, YAML, or XML.}
        \resumeItem{Wrote parsing logic in Rust by constructing an Abstract Syntax Tree, utilising the pulldown-cmark pull parser.}
        \resumeItem{Created bindings for Node.js and Python, with a GitHub workflow that publishes to NPM, PyPi, and Crates.io.}
			\resumeItemListEnd
			
	\resumeSubHeadingListEnd

% -------------------------------- EXPERIENCE -------------------------------- %
\section{\textbf{Work History}}
  \resumeSubHeadingListStart

	  % ! Computer Science Intern - Hawthorn FC
	  \resumeSubheading
      {Computer Science Intern}{August 2025 -- October 2025}
      {Hawthorn Football Club}{Mulgrave, VIC}
      \resumeItemListStart
        \resumeItem{Mentored by the tech and data GM, tasked to build a workflow optimisation project to assist the coaching staff.}
        \resumeItem{Enterprise AI integration using Google Agentspace within GCP to facilitate data analysis for AFL coaching staff.}
        \resumeItem{Implemented tabular RAG for transactional AFL data offered by ChampionData hosted on Snowflake Cloud.}
        \resumeItem{Integrated tailored AI agents and ML models using the Google Agent Development Kit (ADK) and Vertex AI.}
        \resumeItem{Delivered a presentation on prompt engineering for coaches outlining how to prompt LLMs effectively.}
        \resumeItem{Developed a one-shot data analysis workflow for the data analysts built using Claude Code subagents.}
      \resumeItemListEnd

    \vspace{2pt}

	  % ! Software Engineer - Plandid
	  \resumeSubheading
		  {Software Engineer}{July 2025 -- Present}
		  {Plandid}{Remote, VIC}
		  \resumeItemListStart
        \resumeItem{Developed the backend using Python, FastAPI, Pydantic, and SQLAlchemy, exposing APIs to the frontend.}
        \resumeItem{Designed a 40-table PostgreSQL schema with optimised indexes reducing query time by 40\%.}
        \resumeItem{Architected a modular backend structure to ensure strict separation of concerns and scalability.}
        \resumeItem{Implemented secure Google Calendar sync with encrypted storage and CSRF protection.}
        \resumeItem{Integrated Google Places API to aggregate external reviews alongside internal user reviews.}
	    \resumeItemListEnd

    \vspace{2pt}

    % ! Automation Developer - Digimaker
    \resumeSubheading
      {Automation Developer}{March 2025 -- June 2025}
      {Digimaker}{Eastern Suburbs, VIC}
      \resumeItemListStart
        \resumeItem{Identified a bottleneck in the student reporting process and engineered an automation to generate PDF reports.}
        \resumeItem{Wrote JavaScript code in the Google Apps Script environment for a zero-cost student reporting solution.}
        \resumeItem{Optimised script execution flow to handle high-volume batch processing within the strict execution time limits.}
        \resumeItem{Deployed a web interface allowing non-technical admins to trigger report generation and manage student data.}
        \resumeItem{Implemented CI/CD using Github Actions, utilising clasp and git for local development and version control.}
        \resumeItem{Wrote unit tests using Jest for an automated test suite that runs before deployment in production.}
      \resumeItemListEnd

    \vspace{2pt}

    % ! Programming Tutor - Digimaker
    \resumeSubheading
      {Programming Tutor}{October 2024 -- Present}
      {Digimaker}{Eastern Suburbs, VIC}
      \resumeItemListStart
      	\resumeItem{Teaching weekly Python, Java, C \& JavaScript classes to primary school students across 8 different schools, achieving an average 90\% in-class completion rate for my students.}
        \resumeItem{Used supplied lesson sheets to break down core coding concepts, allowing students to independently learn.}
        \resumeItem{Provided patient coding guidance to students when debugging, quickly identifying logic errors and bugs.}
        \resumeItem{Schools: Leibler Yavneh College, McKinnon PS, Ruskin Park PS, Mulgrave PS, Burwood East PS, Greythorn PS ...}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% ------------------------------- VOLUNTEERING ------------------------------- %
\section{\textbf{Volunteering}}
	\resumeSubHeadingListStart
    % ! Monash Assistive Tech Team
    \resumeSubheading
    {AI Engineer}{August 2025 - Present}
    {Monash Assistive Tech Team (student team)}{Clayton, VIC}
      \resumeItemListStart
        \resumeItem{Collaborated on PhD-led research into responsible conversational AI to support individuals with disabilities.}
        \resumeItem{Evaluated ML approaches and papers for emotional intelligence and communication pattern recognition.}
        \resumeItem{Built an agentic AI application using Python, FastAPI, LangChain, and LangGraph.}
        \resumeItem{Experimented with emoji similarity search using PyTorch embeddings and sentence transformers.}
        \resumeItem{Implemented AI as a Judge evaluation patterns to benchmark model performance.}
      \resumeItemListEnd

    \vspace{2pt}

    % ! Monash Connected Autonomous Vehicle
    \resumeSubheading
    {Software Engineer (Urban Autonomy Team)}{August 2025 -- Present}
    {Monash Connected Autonomous Vehicle (student team)}{Clayton, VIC}
      \resumeItemListStart
        \resumeItem{Final year project, a SIL simulation framework bridging the ROS 2 autonomy stack with a ride-hailing app.}
        \resumeItem{Designed a concurrent Rust backend architecture for real-time vehicle telemetry ingestion using WebSockets.}
        \resumeItem{Engineered ROS to HTTP bridges to translate Autoware topics into external JSON endpoints.}
        \resumeItem{Authored the technical proposal and feasibility analysis, utilising the Spiral Model to mitigate integration risks.}
        \resumeItem{Designing a data pipeline, utilising Apache Kafka for ingestion of vehicle route performance and emissions data.}
      \resumeItemListEnd

    \vspace{2pt}

		% ! WIRED (Faculty of Information Technology)
		\resumeSubheading
		{Project Lead}{May 2024 -- June 2025}
		{Faculty of Information Technology Society (student society)}{Clayton, VIC}
			\resumeItemListStart
				\resumeItem{Led a team of 8 students to build projects that benefit the student community at Monash University.}
				\resumeItem{Mentored colleagues in full-stack and project maintainance best practices for version control and pull requests.}
        \resumeItem{Facilitated a productive and inclusive team environment, prioritising time management to fit the busy uni schedule.}
				\resumeItem{Oversaw project timelines using Jira, defining \& monitoring issues, epics, and sprint goals.}
			\resumeItemListEnd

    \vspace{2pt}

		% ! Monash Innovation Guarantee
		\resumeSubheading
		{Monash Innovation Guarantee}{January 2025}
		{UNICEF/Hashcode}{Docklands, VIC}
			\resumeItemListStart
        \resumeItem{Architected a secure SaaS solution for UNICEF's uSupport platform to enhance data privacy.}
        \resumeItem{Pitched the technical proposal to primary stakeholders, achieving a High Distinction grade.}
			\resumeItemListEnd

    \vspace{2pt}

		% ! Computer Science Youtube Channel
		\resumeSubheading
		{Computer Science YouTube Channel}{July 2023 -- October 2024}
		{\href{https://www.youtube.com/@ferdinandcoding}{@ferdinandcoding}}{Online}
			\resumeItemListStart
				\resumeItem{Produced educational videos on algorithms, data structures, and theoretical computer science.}
				\resumeItem{Grew the channel to over 700 subscribers and accumulated a total of 500K+ views.}
				\resumeItem{Simplified computer science topics for a broad audience via short form and long form content.}
			\resumeItemListEnd
	\resumeSubHeadingListEnd

% ------------------------ LICENSES AND CERTIFICATIONS ----------------------- %
\section{\textbf{Licenses \& Certifications}}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \item{
        \begin{tabularx}{\linewidth}{@{}l@{\hspace{0.5cm}}X@{}}
          \textit{Australian Computer Society} & Associate Member \\[1pt]
          \textit{Victorian Government} & Working with Children Check \\[1pt]
          \textit{NVIDIA} & Developer Program Member \\[1pt] 
          \\
          \textit{Google} & Introduction to Agentspace \\[1pt]
          \textit{LangChain} & Deep Agents with LangGraph \\[1pt]
          \textit{Accenture UK} & Developer \& Technology Job Simulation \\[1pt]
          \textit{Commonwealth Bank} & Software Engineering Job Simulation \\[1pt]
          \textit{J.P. Morgan} & Software Engineering Job Simulation
        \end{tabularx}
      }
    }
  \end{itemize}
% ----------------------------- TECHNICAL SKILLS ----------------------------- %
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textit{Languages:}{ C, C++, C\#, Python, Go, Rust, Java, JavaScript, TypeScript, HTML/CSS/SCSS, SQL, JSX, Kotlin.} \\
     \textit{Technologies:}{ React, React Native, Next.js, Angular, Node.js, Docker, MongoDB, PostgreSQL, Flask, FastAPI, Express.} \\
     \textit{Tools:}{ Git, NPM, UV, Yarn, Powershell, Linux, VS Code, Firebase, GCP, AWS, Akamai, Snowflake, Oracle SQL Developer, Jira.} \\
     \textit{Libraries:}{ pandas, numpy, matplotlib, sklearn, langchain, numpy, ngx-graph, RxJS, Socket.IO, JUnit, pytest, Jasmine.} \\
     \textit{UI Libraries:}{ Bootstrap, Material-UI, PrimeNG, ChakraUI, NextUI, Ant Design, Tailwind CSS, Shadcn UI.} \\
     \textit{Concepts:}{ Algorithms, Data Structures, Theoretical CS, Full-Stack Development, CI/CD, DevOps, Database Management.}
    }}
 \end{itemize}

\end{document}
